###BY Category###
```{r setup, include = FALSE, cache = TRUE}
knitr::opts_chunk$set(
  echo    = FALSE,
  warning = FALSE,
  message = FALSE,
  cache   = TRUE
)

# ---- packages ---------------------------------------------------------------
# Install only if missing (do NOT re-install on every knit).
need <- c("dplyr", "tidyr", "readr", "stringr", "htmltools", "DT", "knitr")
new  <- setdiff(need, rownames(installed.packages()))
if (length(new)) install.packages(new, repos = "https://cloud.r-project.org")
invisible(lapply(need, library, character.only = TRUE))

# ---- load codebook ----------------------------------------------------------
# codebook.csv must live next to this Rmd when you render it.
codebook <- readr::read_csv("Codebook/codebook.csv", show_col_types = FALSE) |>
  dplyr::mutate(
    label    = dplyr::coalesce(label, ""),
    measure  = dplyr::coalesce(measure, ""),
    values   = dplyr::coalesce(values, ""),
    projects = dplyr::coalesce(projects, "")
  )

# ---- project badge helpers --------------------------------------------------
project_colors <- c(
  POWERED = "#1f77b4",   # blue
  MAXED   = "#e67e22",   # orange
  MR21    = "#2ecc71"    # green
)

# Vectorised: build every badge HTML in one pass (much faster than per-row).
project_badges_vec <- function(projs_csv) {
  out <- character(length(projs_csv))
  for (i in seq_along(projs_csv)) {
    s <- projs_csv[[i]]
    if (is.na(s) || !nzchar(s)) { out[i] <- ""; next }
    parts <- trimws(strsplit(s, ",", fixed = TRUE)[[1]])
    cols  <- project_colors[parts]
    cols[is.na(cols)] <- "#7f8c8d"
    out[i] <- paste0(
      sprintf(
        '<span style="display:inline-block;padding:2px 8px;margin:1px 2px;border-radius:10px;background:%s;color:#fff;font-size:0.8em;font-weight:600;letter-spacing:0.5px;">%s</span>',
        cols, parts
      ),
      collapse = " "
    )
  }
  out
}

# Single DT-based renderer used by every chapter.
# DataTables is client-side JS: the render cost is constant regardless of
# row count, and the user gets search/sort/paginate for free.
render_category <- function(cat_name, page_length = 25) {
  sub <- codebook |>
    dplyr::filter(category == cat_name) |>
    dplyr::arrange(measure, variable)
  if (nrow(sub) == 0) {
    return(htmltools::HTML("<em>No variables in this category.</em>"))
  }
  tbl <- data.frame(
    Variable = sprintf("<code>%s</code>", htmltools::htmlEscape(sub$variable)),
    Label    = htmltools::htmlEscape(stringr::str_trunc(sub$label, 200)),
    Measure  = htmltools::htmlEscape(sub$measure),
    `Value / coding` = htmltools::htmlEscape(stringr::str_trunc(sub$values, 180)),
    Projects = project_badges_vec(sub$projects),
    check.names = FALSE,
    stringsAsFactors = FALSE
  )
  DT::datatable(
    tbl,
    escape    = FALSE,
    rownames  = FALSE,
    filter    = "top",
    class     = "stripe hover compact",
    options   = list(
      pageLength = page_length,
      autoWidth  = FALSE,
      dom        = "ftip",
      columnDefs = list(
        list(width = "180px", targets = 0),   # Variable
        list(width = "120px", targets = 4)    # Projects
      )
    )
  )
}
```

# Overview {-}

This codebook documents variables from three studies — **POWERED**, **MAXED**, and **MR21** — grouped into six conceptual categories, with a seventh *Administrative / Other* appendix for REDCap system fields (timestamps, record IDs, form completion flags, consent/signature fields, etc.). Each variable is tagged with the project(s) in which it appears:

```{r project-legend, results = 'asis'}
htmltools::HTML(project_badges_vec("POWERED,MAXED,MR21"))
```

Each chapter below has one searchable, sortable, filterable table. Use the column filters at the top of each table to narrow by Measure or Project.

```{r summary-table}
codebook |>
  dplyr::count(category, name = "Variables") |>
  dplyr::arrange(dplyr::desc(Variables)) |>
  dplyr::rename(Category = category) |>
  DT::datatable(options = list(dom = "t", pageLength = 10), rownames = FALSE)
```

```{r project-summary}
codebook |>
  tidyr::separate_rows(projects, sep = ",") |>
  dplyr::mutate(projects = trimws(projects)) |>
  dplyr::filter(projects != "") |>
  dplyr::count(category, projects) |>
  tidyr::pivot_wider(names_from = projects, values_from = n, values_fill = 0) |>
  dplyr::rename(Category = category) |>
  DT::datatable(options = list(dom = "t", pageLength = 10), rownames = FALSE)
```

---

# Demographics

Age, sex assigned at birth, gender identity, pronouns, race/ethnicity, education, household characteristics, and other participant background variables.

```{r demographics}
render_category("Demographics")
```

# Anthropometric Measures

Height, weight, BMI, Tanner staging, and pubertal development indicators.

```{r anthro}
render_category("Anthropometric Measures")
```

# Medical History

Medical diagnoses, surgeries, hospitalizations, medications, menstrual history, substance use, vitals, and prior weight history.

```{r medhx}
render_category("Medical History")
```

# Mental Health Diagnosis

Diagnostic interviews and standardized symptom measures — DIAMOND, BDI-II, PHQ-9, GAD-7, RCADS, YBOCS, OCI, Columbia SSRS, DSM-5 Cross-Cutting Symptoms, MMSE.

```{r mhdx}
render_category("Mental Health Diagnosis")
```

# Eating Disorder Behaviors

EDE, EPSI, ED100K / ED100K+, ED History, Drive for Thinness/Muscularity, Compulsive Exercise, Exercise Dependence, ART, Goldfarb Fear of Fat, Analogous Exercise Decisions, SRHI (habitual eating), post-interview target-weight survey, and binge / purge / restrict / food-intake / milkshake task items from the visit forms.

```{r edbx}
render_category("Eating Disorder Behaviors")
```

# Socio-behavioral

Anxiety, mood, emotion regulation, perfectionism, social evaluation, body image state, interoception, and other transdiagnostic trait / state measures — ASI, BIS/BAS, DERS, Frost MPS, IUS, Self-Compassion, SATAQ, BFNE, Perceptions of Teasing, SPSRQ, FADE/FAMB, NVS, PVS, EMA, OCYC Maladaptive, Body Appreciation.

```{r sociobeh}
render_category("Socio-behavioral")
```

# Administrative / Other {-}

REDCap system fields and study-flow variables: survey timestamps, record IDs, form-complete flags, consent/signature fields, visit start/end times, payment records, and interviewer notes. Included for completeness; not substantive measures.

```{r admin}
render_category("Administrative / Other")
```

# Notes & caveats {-}

- **Mixed intake forms** (DCF, DCF-Parents, Study Visit A/B/C Collection Forms) are split heuristically; review entries flagged in *Administrative / Other* to confirm none should be promoted to a substantive category.
- **Duplicate variable names** across projects are collapsed into a single row with all source projects listed as badges. If the same name refers to different constructs in different projects, split them in `codebook.csv` before rendering.
- **Value coding** is reproduced from the source REDCap export and truncated to 180 chars in the category tables — full strings are preserved in `codebook.csv`.
- **ART (Athletes' Relationship with Training)** is placed under *Eating Disorder Behaviors* because of its use in assessing compulsive exercise in ED populations. Move it to *Socio-behavioral* if you prefer a behavioral-trait framing.
- **ASI** is treated as the *Anxiety Sensitivity Index* (socio-behavioral), not an eating-symptom inventory.
- **Tanner Stages / PDS** are treated as anthropometric/maturation indicators. Move them in `codebook.csv` if your analyses treat them as medical history.

To refine categorization, edit `codebook.csv` (hand-correct the `category` column) and re-render.
